bad forecast good decision

### 2020-07-03 notebook/bad-forecast-good-decision.Rmd
more reps, plot distribution

```{r}
library(mdplearning)
Tmax <- 100
x0 <- which.min(abs(states - 6))
reps <- 5
set.seed(12345)

@@

```{r}
fig_ts <- 
  sims %>%
  filter(time < 25) %>%
  ggplot(aes(time, state, col=model, group = interaction(model,reps))) + 
  geom_line(alpha=0.5) 
fig_ts
```

Note that the pattern is not driven merely be differences in the unfished equilibrium.  Compare forecast performance under management:

```{r}
scores <- sims %>%
  mutate(next_state = dplyr::lead(state_index), model = as.integer(model)) %>%
  select(time, state_index, next_state, action_index, model, reps) %>% 
  rowwise() %>%
  mutate(prob =  transitions[[model]][state_index, next_state, action_index] )

scores %>% 
  group_by(reps, model) %>%
  summarise(score = sum(log(prob))) %>%
  group_by(model) %>% summarise(mean_score = mean(score))

>>>>

```{r}
library(mdplearning)
Tmax <- 100
x0 <- which.min(abs(states - 6))
reps <- 100
set.seed(12345)

@@

```{r}
fig_ts <- 
  sims %>%
  filter(time < 25, reps < 5) %>%
  ggplot(aes(time, state, col=model, group = interaction(model,reps))) + 
  geom_line(alpha=0.5) 
fig_ts
```

Note that the pattern is not driven merely be differences in the unfished equilibrium.  Compare forecast performance under management.  Score is the sum of the log probabilities of observed outcomes, given the

```{r}
scores <- sims %>%
  mutate(next_state = dplyr::lead(state_index), model = as.integer(model)) %>%
  filter(model < 3) %>%
  select(time, state_index, next_state, action_index, model, reps) %>% 
  rowwise() %>%
  mutate(prob =  transitions[[model]][state_index, next_state, action_index] ) %>% 
  group_by(reps, model) %>%
  summarise(score = sum(log(prob)))

scores %>% group_by(model) %>% summarise(mean_score = mean(score))

scores %>% mutate(model = as.factor(model)) %>% 
  ggplot(aes(x = score, group = model, fill = model)) +
  geom_histogram(binwidth = 70)
